Tor's Usability for Censorship Circumvention

### 2015-12-10 paper/circumvention-experiment.tex
intro fix

\section{Tor}
\noindent {\bfseries Usability}
Tor is primarily known as the most widely used anonymity tool today. 
For this reason, user studies on Tor have been solely about the usability of Tor as an
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later. \\

\noindent {\bfseries Scoping}
There are still many features of Tor that are left unevaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation,
we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today \cite{faris2008measuring}, with 
some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.\\

\noindent {\bfseries Motivation}
Changing the configuration interface would not require changes to the 
Tor Browser functionality, making any suggested improvements very practical to 
deploy in a short period of time. {\color {red} Additionally, people are just literally
being censored everywhere so a lot of people are using it for this purpose. So 
we want this to be usable for that purpose.}

>>>>

\section{Introduction}
Tor is primarily known as the most widely used anonymity tool today. 
For this reason, user studies on Tor have been solely about the usability of Tor as an
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later. There has been no work done on Tor as a censorship circumvention tool.

There are still many features of Tor that are left unevaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
Although Tor was not designed to be a censorship circumvention tool, users started
to use Tor as a censorship circumvention tool since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and Tor current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

We believe that this is a great opportunity for user research. Censorship circumvention
is not only a common use case, but one Tor was not intended for. Since Tor does not 
track their users in any way or performs A/B testing, making a user study a more
uniquely beneficial source of feedback. Since the interface does not depend on the 
internal functionalities of Tor, changes made to the configuration interface would not 
require huge changes, making any suggested improvements very practical to 
deploy.
